Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-04 article.tex
updated results order/flow

\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are percieveed to directly impact environmental sustainability.
        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

>>>>

\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
